Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-06-27 paper.qmd
fixes to tex for Annalias changes

We call points in the projection that are on the curve $\mathbfit{y}$. From this we can compute the analog equation for the projection as

>>>>

We call points in the projection that are on the curve $\mathbfit{y}$, so that $\mathbfit{y} = \mathbfit{x}P$ for $\mathbfit{x}$ on the \pD{} curve. Then $\mathbfit{y} - \mathbfit{\mu}_p = (\mathbfit{x} - \mathbfit{\mu})P = \mathbfit{s} P^T \Sigma P$, where $\mathbfit{\mu}_p = \mathbfit{\mu} P$ is the projected mean. We then substitute $(\mathbfit{y} - \mathbfit{\mu}_p) (P^T \Sigma P)^{-1}$ for $\mathbfit{s}$ in the previous equation. From this we can compute the analog equation for the projection as
